---
title: "Homework 09"
author: "Shuai Ding"
date: "11/19/2019"
output:
  html_notebook:
    toc: yes
    toc_float: yes
    theme: spacelab
  html_document:
    toc: yes
    toc_float: yes
    theme: spacelab
always_allow_html: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache=FALSE)
```

## 1. Get HTML
```{r}
library(rvest)
wiki <- read_html("https://en.wikipedia.org/wiki/Mitch_McConnell")
wiki
```

## 2. Get the info box

```{r}
info <- html_node(wiki, ".infobox.vcard")
info
```

## 3. Make a data frame

```{r}
library(knitr)
# a) Parse the infobox table HTML you obtained above into a data frame.
# b) Name the columns of the table you obtain key and value.
table_df <- html_table(info, header = FALSE)
colnames(table_df) <- c("key", "value") 
table_df <- data.frame(table_df)
table_df$key[1] = "Full name"
# c) Filter the data frameto the "Full name", "Political Party", and "Children".
df3 <- table_df[table_df$key %in% c("Full name","Political party","Children"),]
df3
```

## 4. Make a function
```{r}
get_wiki_info <- function(url){
  content <- read_html(url)
  info <- html_node(content, ".infobox.vcard")
  table_df <- html_table(info, header = FALSE)
  colnames(table_df) <- c("key", "value") 
  table_df <- data.frame(table_df)
  table_df$key[1] = "Full name"
  if ("Children" %in% table_df$key){
    df <- table_df[table_df$key %in% c("Full name","Political party","Children"),]
  return(df)
  }
  else {
    df <- table_df[table_df$key %in% c("Full name","Political party"),]
    df <- rbind(df, c("Children",NA))
    return(df)
  }
}
get_wiki_info("https://en.wikipedia.org/wiki/Tammy_Duckworth")
get_wiki_info("https://en.wikipedia.org/wiki/Susan_Collins")
```

## 5. Get all senators' pages

>a) On this page (https://en.wikipedia.org/wiki/Current_members_of_the_United_States_Senate) you find a list of all current senators of the U.S. congress.

```{r}
library(xml2)
library(rvest)
html <- read_html("https://en.wikipedia.org/wiki/Current_members_of_the_United_States_Senate")
links<-html %>%
  html_nodes("#senators") %>% 
  html_nodes(".vcard") %>% 
  html_node("a") %>% 
  html_attr("href") 
print(typeof(links))
```

>b) Create a loop that uses your get_wiki_info function to import the information on political party and number of children for all members of the senate.

```{r}
df_finish <- data.frame(Name=character(),
                   PoliticalParty = character(),
                   Children = integer(),
                   stringsAsFactors=FALSE)
                   
for (each in links) {
  url = paste("https://en.wikipedia.org",each,sep="")
  df <- get_wiki_info(url)
  df <- data.frame(Name = df$value[1],
                   PoliticalParty = df$value[2],
                   Children = df$value[3])
  df_finish <- rbind(df_finish,df)
}
df_finish
```


>c) Clean up your data to provide some summary statistics. How many children does the average senator have? What about by party affiliation?

#### 2.31 children the average senator have. 
#### Republican: 2.62 children the average republican senator have.
#### Democratic: 1.89 children the average democratic senator have.

```{r}
library(dplyr)
library(stringr)
# change records for children as numeric 
a <- c(9,13,30,36,41,43,49,56,59,61,88,90,95)
b <- c(1,4, 1, 1, 2, 3, 4, 1, 2, 1, 5, 1,3)
df_finish$Children[a] <- b
#df_finish
#df_finish[is.na(df_finish)] <- 0
print(summary(df_finish))
```

```{r}
Rep <- df_finish[str_detect(df_finish$PoliticalParty, "Republican"),] 
print(summary(Rep))
```

```{r}
Dem <- df_finish[str_detect(df_finish$PoliticalParty, "Democratic"),] 
print(summary(Dem))
```












