---
title: "The BestBuyExplore API Package Explained"
author: "Shuai Ding"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The BestBuyExplore API Package Explained}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `BestBuyExplore` package contains three functions: `Search_TV_Brand`, `Search_Store` and `Search_Trending_OpenBox`.

## `Search_TV_Brand` Function

The `Search_TV_Brand` function allows the user to enter a brand name of TV. It will return a dashboard listing all characteristics of that brand and sort by the best-selling products over the last week in Best Buy.

```{r, echo=TRUE}
library(BestBuyExplore)
#Search_TV_Brand("Sony", TRUE,TRUE)
# This function returns an shiny dashboard. so it cannot be displayed here.
```

## `Search_Store` Function

This function returns stores information for all Best Buy stores within the radius of the given postal code.

```{r, echo=TRUE}
Search_Store(10025, 20)
```

## `Search_Trending_OpenBox` Function

This function allows the user to enter a specific category. It searches trending products within the given category and returns specific number of trending products with Open Box service.

```{r}
Search_Trending_OpenBox()
```




