---
title: "Homework 10"
author: "Shuai Ding"
date: "11/29/2019"
output:
  html_notebook:
    toc: yes
    toc_float: yes
    theme: spacelab
  html_document:
    toc: yes
    toc_float: yes
    theme:  spacelab
always_allow_html: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache=FALSE)
```

```{r}
library(DBI)
witch_con <- dbConnect(
  RMySQL::MySQL(),
  user = 'student',
  password = 'mds-is-fun',
  dbname = 'witchcraft',
  host = 'tbrambor.csbmzoea3lu9.us-east-1.rds.amazonaws.com',
  port = 3306
)
```

## 1. Getting to know the data
#### a) Show a list of the tables included in the database.

```{sql, connection="witch_con"}
SHOW TABLES
```

#### b) Display the column names for the table accused.
```{sql, connection="witch_con"}
SHOW COLUMNS FROM accused
```

#### c) How many people are included in the accused table?
```{sql, connection="witch_con"}
SELECT COUNT(*)
FROM accused
WHERE firstname is NOT NULL or lastname is NOT NULL
```

> 3218 people are included in the accused table

#### d) Display the columns firstname, sex, and age for 5 cases in the accused table.
```{sql, connection="witch_con"}
SELECT firstname, sex, age
FROM accused
LIMIT 5;
```

#### e) Looks like the age is missing for some observations. Count the number of nonmissing values for age in the data.
```{sql, connection="witch_con"}
SELECT COUNT(age)
FROM accused
WHERE age IS NOT NULL
```

> 166 nonmissing values for age in the data

### f) Show a list of unique occupations.

```{sql, connection="witch_con"}
SELECT DISTINCT occupation
FROM accused
WHERE occupation IS NOT NULL
```

## 2. Seeing the Devil
#### a) List the unique devil_types in the data.
```{sql, connection="witch_con"}
SELECT DISTINCT devil_type
FROM devilappearance
```

#### b) How many of the sightings mention the word "black" in the description?
```{sql, connection="witch_con"}
SELECT COUNT(devil_text)
FROM devilappearance
WHERE devil_text LIKE '%black%'
```

> 121 sightings mention the word "black" in the description.

#### c) What proportion of the devils (in devil_type) are male?

```{sql, connection="witch_con"}
SELECT COUNT(*) / (SELECT COUNT(*)
FROM devilappearance
WHERE devil_type IS NOT NULL) as proportion
FROM devilappearance
WHERE devil_type = 'Male' or devil_type = 'Male Fairy' 
```
> 65.7% % of the devils are male.


```{sql, connection="witch_con"}
SELECT COUNT(*) / (SELECT COUNT(*)
FROM devilappearance) as proportion
FROM devilappearance
WHERE devil_type = 'Male' or devil_type = 'Male Fairy' 
```
> 65.4% % of the devils are male (NULL included).

## 3. The trial
#### a) What are the average and maximum numbers of male and female accusers?
```{sql, connection="witch_con"}
SELECT AVG(female_accusers),  MAX(female_accusers), AVG(male_accusers), MAX(male_accusers)
FROM   trial 
```

#### b) Count the number of sentences by sentence type. List them in a table (in descending order), excluding missing values. Rename the column headings to something sensible.
```{sql, connection="witch_con"}
SELECT sentence, COUNT(*) AS "Number of sentences"
FROM trial
WHERE sentence IS NOT NULL
GROUP BY sentence
ORDER BY 2 DESC;
```

#### c) Do the number of accusers matter for the verdict? Compare the average number of accusers by the type of verdict. Again make sure the table is sorted and the headings make sense.

```{sql, connection="witch_con"}
SELECT verdict, 
       AVG(female_accusers)+AVG(male_accusers) as 'Average number of accusers'

FROM trial
WHERE verdict IS NOT NULL
GROUP BY verdict
ORDER BY 1 DESC;
```

## 4. Tortured Truth
#### a) Left join the trial and confession tables. For what share of trials does the database record confessions? Create a results table with the number of all trials, the number of confessions, and the share of trials with confessions recorded.
```{sql, connection="witch_con"}
SELECT COUNT(trial.trialref),COUNT(confession.trialref),
COUNT(confession.trialref)/COUNT(trial.trialref) as 'Share'

FROM trial LEFT OUTER JOIN confession
  ON confession.trialref = trial.trialref  
```















