---
title: "Homework 04"
author: "Shuai Ding"
date: "10/10/2019"
output:
  html_notebook:
    toc: yes
    toc_float: yes
    theme: spacelab
  html_document:
    toc: yes
    toc_float: yes
    theme:  spacelab
always_allow_html: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache=FALSE)
```

## 1. Functions in the dplyr Package
### a) Longest name
```{r}
library(dplyr)
library(purrr)
library(DT)
content <- mget(ls("package:dplyr"), inherits = TRUE)
dplyr_functions <- Filter(is.function,content)
```

```{r}
name_f <- map(dplyr_functions, names) %>%
  names()
#name_f
len <- map_int(name_f,nchar)
m <- max(len)
for (name in name_f) {
  if (nchar(name) == m) {
    print(name)
  }
}
```
> The function named "group_by_drop_default" has the longest name.

### b) Number of arguments
```{r}
argument <- map(dplyr_functions, formals) 
arg <- map(argument,names) 
#arg[[2]][2]

arg_1 <- sapply(arg, length)
max(arg_1)

a <- head(arg_1[order(-unlist(arg_1))], n=10) 
b <- as.data.frame(a)
DT::datatable(b)
```
### c) Most common argument
```{r}
new_df <- as.data.frame(matrix(data = NA, nrow = 1, ncol = 1))
for (i in 1:length(dplyr_functions)) {
  for (j in 1:length(argument[[i]])) {
    new_df <- rbind(new_df, print(names(argument[[i]][j])))
  }
}
new_df <- new_df %>%
  group_by(V1) %>%
  summarise(count_func = n()) %>%
  arrange(desc(count_func))
head(new_df, n=5)  
```

> The most common argument named "...", which allows users not to specify the name of the argument. This argument will pass arguments to the functions and can be numbers or variety of arguments. 

## 2. Infant Mortality and GPD per Capita
### a) Highest and lowest infant mortality rates in 2018

```{r}
library(WDI)

df <- WDI(country='all', indicator=c("NY.GDP.PCAP.PP.KD", "SP.DYN.IMRT.IN"), extra=TRUE, start = 1960, end = 2018)
#df
df1 <- rename(df, gdpcap = NY.GDP.PCAP.PP.KD, infmort = SP.DYN.IMRT.IN)
#df1

df2<- na.omit(df1)
#df2

df3 <- filter(df2, region != "Aggregates")
#df3
df4 <- arrange(df3, desc(infmort)) %>% filter(year == '2018') 
high <- head(df4, n=5)
df5 <- arrange(df3,infmort) %>% filter(year == '2018') 
low <- head(df5,n=5)
finish_country <- rbind(high, low) %>% arrange(desc(infmort)) %>% select(country, infmort, gdpcap)
finish_country
```

### b) Overall regression

```{r}
library(ggplot2)
summary(lm(infmort ~ gdpcap, data = df2))
ggplot(df2, aes(x = gdpcap, y = infmort)) + geom_point() +
  geom_point( alpha = .4)+
  geom_smooth()+
  labs(x = "GDP per capita", y = "Infant mortality (per 1000 live births", title = "Correlation between infant mortality and GDP per capita") +
  theme(plot.title = element_text(hjust = 0.5))

```


> The scatter plot indicates that when GDP per capita is smaller than approximately 10000, infant mortality was high than 100 per 1000 live births. Then,infant mortality takes a steep decrease and becomes flat with GDP become higher than 10000.

### c) Regression by region

```{r}
df_region <- split(df2, df2$region)
str(df_region)

df7 <- df2 %>% 
  split(df2$region) %>%
  map(~ lm(infmort ~ gdpcap, data = .)) %>%
  map(~ coef(.)) %>%
  map_dbl("gdpcap")

df_coef <- as.data.frame(sort(df7) )
df_coef

```

### d) Regression by country

```{r}
df_country <- split(df3, df3$country)
#str(df_country)
lr_country <- map(df_country, ~ lm(infmort ~ gdpcap, data = .)) %>%
  map(summary)

#df3
lr0 = df3 %>%
  group_by(country) %>%
  group_modify(.f = ~broom::tidy(lm(infmort ~ gdpcap, data = .)))
                               
lr1 = df3 %>%
  group_by(country) %>%
  group_modify(.f = ~broom::tidy(lm(infmort ~ gdpcap, data = .), conf.int = 0.95))

lr2 <- lr1 %>% 
  select(country, estimate, term) %>%
  filter(term == 'gdpcap') %>%
  filter(estimate > 0)
summary(lr2)
# 14 countries indicate positive relation
lr3 <- lr0 %>% 
  filter(term == 'gdpcap') %>%
  select(country, estimate)
lr3
ggplot(data = lr3, aes(x=estimate)) + geom_histogram()


```


> 14 (6.09%) countries have positive relation, which are most at odds with the overall regression estimated in part(b).

### e) Added squared term

```{r}
finish_1 = df3 %>%
  group_by(country) %>%
  group_modify(.f = ~ broom::glance(lm(infmort ~ gdpcap, data = .))) %>%
  select(country, origin = adj.r.squared)
gdp_2 = df3$gdpcap
finish_2 = df3 %>%
  mutate(gdpcap_squ = (gdp_2 * gdp_2)) %>%
  group_by(country) %>%
  group_modify(.f = ~ broom::glance(lm(infmort ~ gdpcap + gdpcap_squ, data = .))) %>%
  select(country, square_gdp = adj.r.squared)
#finish_2

finish <- full_join(finish_1, finish_2) %>%
  dplyr::ungroup(.) %>%
  filter(square_gdp > origin)
finish
```

> For aforementioned countries in the table, r squared increases. And for 155 countries out of 186 countries show better predicting performance, I recommend to keep squared term. 












